Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2): Submission, Peer-Review, and Sorting Process, and Results

### 2014-11-04 WSSSPE2_preworkshop_report/WSSSPE2_review_report.tex
adding section on other parts of the meeting

>>>>

\section{Other parts of the workshop}

WSSSPE2 will include two keynote presentations, and lightening talks from accepted paper authors, in addition to a set of breakout sessions.  The breakouts will allow attendees to participate in discussions about sustainability, future actions, and two of the five areas that resulted from the community submission, review, and grouping process.  There will also be reporting from the breakout groups to collect information for all attendees, as well as people who were not able to attend, to understand the discussions.
